Geodesic Flow on the Necker Cube Surface

### 2017-07-01 paper.tex
63017

\subsection{The Euclidean cone surface $\mathbf{M}$}
\compat{I would say: Observe that translations of ${\mathbb R}^2$ by pairs even integers preserves the subset ${\mathbf P}$ and respects the equivalence relation defining ${\mathbf U'}$. Thus this gives an action of $(2{\mathbb Z})^2$ on ${\mathbf U}'$. We define ${\mathbf M}$ to be the quotient. It is depicted in Figure ...}

@@

The quotient space is a genus 1 surface that resembles a $2\times2$ torus with a unit square removed from it. Near the outer vertex it behaves as a torus might. The inner vertices $c_{1},c_{3}$ have cone angle $\frac{3\pi}{2}$, and $c_{2}$ has a cone angle of $3\pi$. None of these vertices are integral multiples of $2\pi$, so in order to create a translation surface we have to take a minimal number of copies of the quotient space so every vertex has a cone angle that is a multiple of $2\pi$. \compat{Move the discussion of building the translation surface to the next section. Otherwise this paragraph is good.}

\newpage
\subsection{Translation Surface}
\compat{You need to build the surface out of pieces rather than out of ``copies of $\mathbf{M}$.''} 
We will now define a translation which is a four-fold branch cover of $\mathbf{M}$. To each copy we associate a direction of the flow under indices \{0,1,2,3\}. Let $\mathbf{M}_{0} $ denote the quotient space with its vertices removed:

\begin{center}
\includesvg[width=2in]{branchvert}
\end{center}

Now denote the set of singularities of $\mathbf{M}_{0}$ by $\Sigma$, where $\Sigma=\{s_{i}:i=1,...,8\}$. We let $ H_{1} (\mathbf{M}_{0}, \Sigma ; \mathbb{Z} / 4 \mathbb{Z}) =\{\gamma,e\}$ be the homology group

\compav{Little stuck on how to actually write this out.}

\begin{figure}[H]
\begin{center}
\includesvg[width=4in]{branchcover}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includesvg[width=4in]{branchcoverchopped}
\end{center}
\end{figure}

>>>>

\subsection{The Euclidean cone surface $\mathbf{M}$}
\compat{I would say: Observe that translations of ${\mathbb R}^2$ by pairs even integers preserves the subset ${\mathbf P}$ and respects the equivalence relation defining ${\mathbf U}$. Thus this gives an action of $(2{\mathbb Z})^2$ on ${\mathbf U}'$. We define ${\mathbf M}$ to be the quotient. It is depicted in Figure ...}

Observe that the translations by pairs of even integers preserves the subset $\mathbf P$ and respects the equivalence relation on $\mathbf U$

@@

The quotient space is a genus 1 surface that resembles a $2\times2$ torus with a unit square removed from it. Near the outer vertex it behaves as a torus might. The inner vertices $c_{1},c_{3}$ have cone angle $\frac{3\pi}{2}$, and $c_{2}$ has a cone angle of $3\pi$. None of these inner vertices have cone angles that are integral multiples of $2\pi$, so in order to create the necessary translation surfaces we require the minimal number of copies of both $\mathbf{U}$ and $\mathbf{M}$ to construct their associated phase spaces.  \compat{Move the discussion of building the translation surface to the next section. Otherwise this paragraph is good.}

\subsection{Four-Fold Cover of $\mathbf{U}$}
A geodesic on our surface can travel in one of four possible directions at any given time. To each phase we associate a numeric label I,II,II, or IV, where I contains the initial and terminal points of a closed geodesic. (Similar to [author]'s construction of phases of the Wind-Tree Model). For every even integer pair that is centered around every hole of $\mathbf{P}$, assign an integer pair (m.n). Identify the edges in the following manner:

\begin{center}
\includesvg[width=4in]{utilda}
\end{center}
This is a branched cover of $\mathbf{U}$ of degree four that can be thought of as four copies of $\mathbf{P}$, all stacked on one another with the following identifications:
\begin{center}
$([2m-\frac{1}{4}, 2m+\frac{1}{4}], 2n-\frac{1}{4},j)\sim(2m-\frac{1}{4},[2n-\frac{1}{4}, 2n+\frac{1}{4}],j+\bar{1})$\\
\vspace{0.2in}$([2m-\frac{1}{4}, 2m+\frac{1}{4}], 2n+\frac{1}{4},j)\sim(2m+\frac{1}{4},[2n-\frac{1}{4}, 2n+\frac{1}{4}],j+\bar{1})$\\
\vspace{0.2in}For (m,n,j) $\in \mathbb{Z}^{2}\times\mathbb{Z}/4\mathbb{Z}$
\end{center}
There are four distinct vertices for each hole centered at (m,n) on  $\mathbf{P}\times\mathbb{Z}/4\mathbb{Z}/\sim$ of cone angle $6\pi$. To create  $\mathbf{U}$'s translation surface that still behaves as a proper cover of $\mathbf{U}$, we define a map  $p:(\mathbf{P}\times\mathbb{Z}/4\mathbb{Z}/\sim) \rightarrow \tilde{\mathbf{U}}$ as

\begin{equation}
	p\left[\begin{array}{c}
		u\\v\\z
	\end{array}\right] =
		\left[ \hspace{1mm} \begin{matrix}
				1 & 0 \\
				0 & -1 \\
			\end{matrix}\hspace{1mm}\right]^{z}\left[\begin{array}{c}
					u\\v
				\end{array}\right]\times\{z\}.
\end{equation}

\compav{So I'm not sure if I can actually define p on}
 $\mathbf{P}\times\mathbb{Z}/4\mathbb{Z}/\sim$

p preserves the edge identification by affine transformations (rotating every phase plane about its origin according to its phase value).  $\tilde{\mathbf{U}}$ as a translation cover:

\begin{figure}[H]
\centering
\includesvg[width=4in]{utildaprime}
\end{figure}
As one might expect, traveling in the same direction in every phase has a different effect on the integer pair (m,n) relative to first phase. A path in that sense is considered closed if it eventually returns to the exact same point, and periodic should it return to the same phase as well.

\newpage
\subsection{Translation Surface}
\compat{You need to build the surface out of pieces rather than out of ``copies of $\mathbf{M}$.''} 
With $\tilde{\mathbf{U}}$ defined, its topological quotient is given by $\tilde{\mathbf{M}}$ = $\tilde{\mathbf{U}}/(2\mathbb{Z})^{2}$.

\begin{figure}[H]
\centering
\includesvg[width=4in]{mtilda}
\end{figure}
$\tilde{\mathbf{M}}$ is also a degree four branched cover of $\mathbf{M}$. A covering map $g:\tilde{\mathbf{M}} \rightarrow \mathbf{M}$ also individually rotates these squares about the centers of their holes according to their labels and maps their points to $\mathbf{M}$.

$\tilde{\mathbf{M}}$ is a genus 5 translation surface with four singularities.

\begin{figure}[H]
\centering
\includesvg[width=4in]{mtildastaircase}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=4in]{cylinderdecomp.pdf}
\end{figure}

\begin{figure}[H]
\centering
\includesvg[width=4in]{cylinderskew}
\end{figure}

\begin{figure}[H]
\centering
\includesvg[pretex=\tiny, width=4in]{slopeonecylinder}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=2in]{commute.pdf}
\end{figure}
